---
title: "Untitled"
author: " "
date: "2026-03-13"
output:
  pdf_document:
    toc: true
    toc_depth: 2
    number_sections: true
---

# Créer les dossiers
```{r, results='hide',warning=FALSE}
dir.create("data")
dir.create("results")

dir.create("results/FastQC")
dir.create("results/MultiQC")
dir.create("results/MACS")
```

# Télécharger les données
## Experiment (FNR IP ChIP-seq Anaerobic A)
```{r, results='hide',warning=FALSE}
if (!file.exists("data/SRR576933.fastq.gz")) {
  download.file(
    url = "ftp://ftp.sra.ebi.ac.uk/vol1/fastq/SRR576/SRR576933/SRR576933.fastq.gz",
    destfile = "data/SRR576933.fastq.gz",
    method = "libcurl"
  )
}
```

## Control (anaerobic INPUT DNA)
```{r, results='hide',warning=FALSE}

if (!file.exists("data/SRR576933.fastq.gz")) {
  download.file(
    url = "ftp://ftp.sra.ebi.ac.uk/vol1/fastq/SRR576/SRR576938/SRR576938.fastq.gz",
    destfile = "data/SRR576938.fastq.gz",
    method = "wget", 
    extra = "-nc"   
  )
}
```


## Escherichia coli str. K-12 substr. MG1655, complete genome (NC_000913.2)
```{r, results='hide',warning=FALSE}
if (!file.exists("data/NC_000913.2.fasta")) {
download.file(
  url = "https://eutils.ncbi.nlm.nih.gov/entrez/eutils/efetch.fcgi?db=nuccore&id=NC_000913.2&rettype=fasta&retmode=text", 
  destfile = "data/NC_000913.2.fasta", 
  method = "libcurl"
  )
}
```

## Escherichia coli str. K-12 substr. MG1655, complete genome (NC_000913.3)
```{r, results='hide',warning=FALSE}
if (!file.exists("data/NC_000913.3.fasta")) {
  download.file(
    url = "https://eutils.ncbi.nlm.nih.gov/entrez/eutils/efetch.fcgi?db=nuccore&id=NC_000913.3&rettype=fasta&retmode=text", 
    destfile = "data/NC_000913.3.fasta", 
    method = "libcurl"
    )
}
```

# Quality control

## Experiment
```{bash, results='hide'}
/opt/anaconda3/bin/fastqc --outdir \
results/fastqc data/SRR576933.fastq.gz &> data/fastqc_SRR576933.sh.log
```

## Control
```{bash, results='hide'}
/opt/anaconda3/bin/fastqc --outdir \
results/fastqc data/SRR576938.fastq.gz &> data/fastqc_SRR576938.sh.log
```

## MultiQC
```{bash, results='hide'}
/opt/anaconda3/bin/multiqc --outdir results/multiqc results/fastqc/ 
```

<!--
# Bowtie
```{r, results='hide',warning=FALSE}
library(Rbowtie)
```

## Prepare the index file
```{r, results='hide',warning=FALSE}
bowtie_build(references = "data/NC_000913.3.fasta",
             outdir = "results/bowtie",
             prefix = "NC_000913.3", 
             force = TRUE)
```
-->

# Bowtie
(The code below works, I tested it on Narval, I just can't install bowtie on my laptop :/)

## Prepare the index file
```{bash, results='hide'}
#bowtie-build data/NC_000913.3.fasta results/bowtie/NC_000913.3
```

## Experiment
```{bash, results='hide'}
#bowtie results/bowtie/NC_000913.3 -q data/SRR576933.fastq.gz  -v 2 -m 1 -3 1 -S 2> results/bowtie/SRR576933.out > results/bowtie/SRR576933.sam
```

## Control
```{bash, results='hide'}
#bowtie results/bowtie/NC_000913.3 -q data/SRR576938.fastq.gz  -v 2 -m 1 -3 1 -S 2> results/bowtie/SRR576938.out > results/bowtie/SRR576938.sam
```











